Enhancement of SDR in Thessaloniki

### 2024-09-02 GHI_enh_read_aod_brewer.tex
Commit 2024-09-01 14:14
Commit 2024-09-02 21:09

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-09-01}

@@

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-54}
\end{figure}

@@

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-09-02}

@@

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-54}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-55}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-55}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-56}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-56}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-57}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-57}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-58}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-58}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-59}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-59}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-60}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-60}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-61}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-61}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-62}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-62}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-63}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-63}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-64}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-64}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-65}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-65}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-66}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-66}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-67}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-67}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-68}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-68}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-69}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-69}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-70}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-70}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-71}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-71}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-72}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-72}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-73}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-73}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-74}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-74}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-75}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-75}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-76}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-76}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-77}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-77}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-78}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-78}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-79}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-79}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-80}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-80}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-81}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-81}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-82}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-82}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-83}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-83}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-84}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-84}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-85}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-85}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-86}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-86}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-87}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-87}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-88}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-88}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-89}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-89}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-90}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-90}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-91}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-91}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-92}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-92}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-93}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-93}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-94}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-94}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-95}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-95}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-96}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-96}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-97}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-97}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-98}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-98}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-99}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-99}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-100}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-100}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-101}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-101}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-102}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-102}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-103}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-103}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-104}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-104}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-105}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-105}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-106}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-106}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-107}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-107}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-108}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-108}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-109}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-109}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-110}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-110}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-111}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-111}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-112}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-112}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-113}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-113}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-114}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-114}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-115}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-115}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-116}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-116}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-117}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-117}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-118}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-118}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-119}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-119}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-120}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-120}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-121}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-121}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-122}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-122}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-123}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-123}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-124}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-124}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-125}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-125}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-126}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-126}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-127}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-127}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-128}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-128}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-129}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-129}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-130}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-130}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-131}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-131}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-132}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-132}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-133}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-133}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-134}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-134}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-135}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-135}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-136}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-136}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-137}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-137}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-138}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-138}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-139}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-139}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-140}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-140}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-141}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-141}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-142}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-142}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-143}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-143}
\end{figure}

@@

\begin{verbatim}
range 0.0001914191 0.2557606 
\end{verbatim}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-144}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-144}
\end{figure}
